On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-08-03 paper.tex
Added relations e1 d1

Let $\Phi$ be a simply-laced irreducible root system of rank $\geq 3$.
Fir $m\geq 2$ denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following
 three families of relations:
\begin{align}
 \label{eq:am} \tag{$a_m$} x_\alpha(\xi) x_\alpha(\eta) & = x_\alpha(\xi+\eta),&  \xi,\eta\in B_k,\ k\leq m;&\\
 \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\alpha'}(\eta))] &  = 1, & \text{in the case $\alpha+\alpha'\not\in\Phi\cup\{0\}$,}\\
 \nonumber                                                     &       & \xi \in B_k,\ \eta \in B_l,\ l,k\leq m;\\
 \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\alpha'}(\eta)] & = x_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi\eta), & \text{in the case $\alpha+\alpha'\in \Phi$,}\\
 \nonumber                                                    &  & \xi \in B_k,\ \eta \in B_l,\ l, k, l+k \leq m.
 \end{align}

Now define the group $G_1$ presented by generators $\mathcal{X}_1$ and the set of relations $\RR{1}$ consisting of 
 the above families of relations $(a_1)$, $(b_1)$, $(c_1)$ with one extra family of relations
\begin{equation} \nonumber \tag{$d_1$}
[[x_{\alpha}(\xi t), x_{\beta}(\eta)],  x_{\gamma}(\zeta t)] = [[x_{\alpha}(\xi t), x_{\beta}(\eta t)],  x_{\gamma}(\zeta)], 
\end{equation}
where $\alpha, \beta, \gamma \in \Phi$ are such that $\alpha+\beta+\gamma \in \Phi$ and $\xi, \eta, \zeta \in A$.

The aim of this subsection is to demonstrate the following analogue of~\cite[Lemma~3.3]{Tu83}. 
\begin{lemma}\label{lem:tul3.3}
 Let $\Phi$ be a simply-laced root systems of rank $\geq 3$. 
 Then the natural inclusion of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces an isomorphism $G_n \to G_{n+1}$ for $n\geq 1$.
 Consequently, the group $\St(\Phi, B)$ is isomorphic to $G_1$.
\end{lemma}
Unfortunately, the lemma cannot be proved by a slight modification of the original short argument of Tulenbayev.
 %for even in the linear case it works only for $\mathrm{rk}(\Phi)\geq 4$, and, in particular, is unsuitable in the case $\Phi=\mathsf{D}_\ell$.
Instead, we have to employ a varition of a much longer argument of U.~Rehmann and C.~Soul{\'e}, cf~\cite{Re75,RS76}.

>>>>

Let $\Phi$ be a simply-laced irreducible root system of rank $\geq 3$.
For $m\geq 1$ denote by $G_m$ the group presented by generators $\mathcal{X}_m$ and the set of relations $\RR{m}$ consisting of the following
 three families of relations:
\begin{align}
 \label{eq:am} \tag{$a_m$} x_\alpha(\xi) x_\alpha(\eta) & = x_\alpha(\xi+\eta),&  \xi,\eta\in B_k,\ k\leq m;&\\
 \label{eq:bm} \tag{$b_m$} [x_\alpha(\xi), x_{\alpha'}(\eta))] &  = 1, & \text{in the case $\alpha+\alpha'\not\in\Phi\cup\{0\}$,}\\
 \nonumber                                                     &       & \xi \in B_k,\ \eta \in B_l,\ l,k\leq m;\\
 \label{eq:cm} \tag{$c_m$} [x_\alpha(\xi), x_{\alpha'}(\eta)] & = x_{\alpha+\alpha'}(N_{\alpha,\alpha'}\xi\eta), & \text{in the case $\alpha+\alpha'\in \Phi$,}\\
 \nonumber                                                    &  & \xi \in B_k,\ \eta \in B_l,\ l, k, l+k \leq m.
 \end{align}

 \begin{lemma} In the group $G_1$ the following two families of relations are equivalent:
\begin{align} \nonumber \tag{$d_1$}
[[x_{\alpha}(a t), x_{\beta}(b t)],  x_{\gamma}(c)] & = [x_{\alpha + \beta}(a b t),  x_{\gamma}(c t)], & a,b,c \in A,\ \alpha + \beta + \gamma \in \Phi\\
\nonumber \tag{$e_1$}
[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta+\gamma \not\in \Phi. \end{align}
 \end{lemma}

The aim of this subsection is to demonstrate an analogue of~\cite[Lemma~3.3]{Tu83}. 
It is clear that the natural embedding of generators $\mathcal{X}_n \subseteq \mathcal{X}_{n+1}$ induces
 a map $\theta_n\colon G_n \to G_{n+1}$ for $n\geq 2$.
\begin{lemma}\label{lem:tul3.3}
 Let $\Phi$ be a simply-laced root systems of rank $\geq 3$.

 Moreover, the map $\theta_1\colon G_1/H \to G_2$ induced by  is isomorphic to $G_1$.
\end{lemma}
Unfortunately, the lemma cannot be proved by a slight modification of the original short argument of Tulenbayev.
 %for even in the linear case it works only for $\mathrm{rk}(\Phi)\geq 4$, and, in particular, is unsuitable in the case $\Phi=\mathsf{D}_\ell$.
Instead, we have to employ a varition of a much longer argument of U.~Rehmann and C.~Soul{\'e}, cf~\cite{Re75,RS76}.
